---
title: "ER Analyses"
author: "JMH"
date: "11/19/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo= FALSE}
library(tidyverse)
library(here)
library(mgcViz)
library(MuMIn)
library(mgcv)
library(forecast)
library(gridExtra)
library(tidymv)
library(ggpubr)
```

# Load & munge data
```{r}
load(file.path(here::here("04_SavedImages"), "02c_ERanalysesPonly_rdat"))
```


```{r message=FALSE, warning=FALSE}
met <- readr::read_csv(file = file.path(here::here("01_Data"),"02_PostERmet.csv")) %>% 
  mutate(stream = fct_relevel(stream, c("st11U", "st18", "st6", "st9")),
         treatment = fct_relevel(treatment, c("ambient", "nitrogen", "phosphorus")),
         Yf = as.factor(Yf),
         streamTreat = as.factor(streamTreat)) %>% 
  filter(treatment == "ambient" | treatment == "phosphorus") %>% 
  droplevels()

# 
# met <- readr::read_csv(file = file.path(here::here("01_Data"),"01_MundgedMetabDat.csv")) %>% 
#   # in gam if a factor is ordered then it compares to a baseline, if not ordered it just makes a different smooth
#   # we want treatment to compare to amb, but no comparisons for stream
#   # https://stat.ethz.ch/R-manual/R-patched/library/mgcv/html/gam.models.html
#   # https://stats.stackexchange.com/questions/447326/if-i-have-five-levels-of-a-categorical-predictor-is-there-any-way-to-get-coeffi
#   mutate(stream = fct_relevel(stream, c("st11U", "st18", "st6", "st9")),
#          treatment = fct_relevel(treatment, c("ambient", "nitrogen", "phosphorus")),
#          Yf = as.factor(Yf),
#          streamTreat = as.factor(streamTreat),
#          ppdoy180 = ifelse(doy <180,"l180", "g180"))%>%
#   # cutting it off here removes most of the weird, low ER values
#   filter(doy >=183) %>%
#   group_by(streamTreat) %>% 
#   dplyr::mutate(DD = cumsum(meanTemp)) %>% 
#   ungroup() %>% 
#   filter(treatment != "nitrogen") %>% 
#   droplevels()

```



# ER Plots
Big differences among treatments. Normalish
```{r echo=FALSE}
ggplot(met, aes(y = lER, x = doy, color = treatment, shape = ppdoy180)) +
  geom_point()+
  stat_smooth() +
  facet_wrap(vars(stream))
```


```{r}
ggplot(met, aes(sample = lER)) +stat_qq() + stat_qq_line() 
```


```{r}
ggplot(met, aes(sample = lER, color = stream)) +stat_qq() + stat_qq_line() +
  facet_grid(.~stream)
```


same as N, best model chosen for all didn't fit
```{r echo= FALSE}
BestERCor <- corARMA(p = 3,q = 0, form = ~ doy | streamTreat)
```


## Model sel

```{r echo=FALSE, include = FALSE}
# # full with stream as temp or category
# g.er.modsel1t <-  uGamm(lER ~ treatment * invKT.C.StMean * Tanom.iktCs +
#                       s(Qres, by = stream) + s(DOYres, by = stream),
#                 correlation = BestERCor, REML = FALSE, data = met,
#                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 500), class = "gamm")
# 
# g.er.modsel1s <-  uGamm(lER ~ treatment * stream  * Tanom.iktCs +
#                       s(Qres, by = stream) + s(DOYres, by = stream),
#                 correlation = BestERCor, REML = FALSE, data = met,
#                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 500), class = "gamm")
# 
# # Qres only with stream as temp or category
# g.er.modsel2t <-  uGamm(lER ~ treatment * invKT.C.StMean * Tanom.iktCs +
#                       s(Qres) + s(DOYres, by = stream),
#                 correlation = BestERCor, REML = FALSE, data = met,
#                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 500), class = "gamm")
# 
# g.er.modsel2s <-  uGamm(lER ~ treatment * stream * Tanom.iktCs +
#                       s(Qres) + s(DOYres, by = stream),
#                 correlation = BestERCor, REML = FALSE, data = met,
#                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 500), class = "gamm")
# 
# # Doy only with stream as temp or category
# g.er.modsel3t <-  uGamm(lER ~ treatment * invKT.C.StMean * Tanom.iktCs +
#                       s(Qres, by = stream) + s(DOYres),
#                 correlation = BestERCor, REML = FALSE, data = met,
#                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 500), class = "gamm")
# 
# g.er.modsel3s <-  uGamm(lER ~ treatment * stream * Tanom.iktCs +
#                       s(Qres, by = stream) + s(DOYres),
#                 correlation = BestERCor, REML = FALSE, data = met,
#                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")
# 
# g.er.Dredge_1t <-  dredge(global.model = g.er.modsel1t, evaluate = TRUE, rank = AIC)
# g.er.Dredge_1s <-  dredge(global.model = g.er.modsel1s, evaluate = TRUE, rank = AIC)
# g.er.Dredge_2t <-  dredge(global.model = g.er.modsel2t, evaluate = TRUE, rank = AIC)
# g.er.Dredge_2s <-  dredge(global.model = g.er.modsel2s, evaluate = TRUE, rank = AIC)
# g.er.Dredge_3t <-  dredge(global.model = g.er.modsel3t, evaluate = TRUE, rank = AIC)
# g.er.Dredge_3s <-  dredge(global.model = g.er.modsel3s, evaluate = TRUE, rank = AIC)
```



```{r echo=FALSE}
g.erDredgeSumt1 <- merge(g.er.Dredge_1t, g.er.Dredge_2t)
g.erDredgeSumtF <- merge(g.erDredgeSumt1, g.er.Dredge_3t)
g.erDredgeSums1 <- merge(g.er.Dredge_1s, g.er.Dredge_2s)
g.erDredgeSumsF <- merge(g.erDredgeSums1, g.er.Dredge_3s)
g.erDredgeSumF <- merge(g.erDredgeSumtF, g.erDredgeSumsF)
```

Model selection for all models
```{r echo=FALSE}
subset(g.erDredgeSumF, delta <= 2)
```

```{r}
g.er.BEST <- gamm(lER ~ treatment * stream + treatment * Tanom.iktCs + stream * Tanom.iktCs  +
                      s(Qres, by = stream) + s(DOYres, by = stream),
                correlation = BestERCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))
```


Stream Temperature models; AIC difference = -31.2
```{r echo=FALSE}
subset(g.erDredgeSumtF, delta <= 2)
```

Best with stream temp
```{r}
g.er.BEST_t <- gamm(lER ~ treatment * Tanom.iktCs + invKT.C.StMean * Tanom.iktCs  + invKT.C.StMean * treatment +
                      s(Qres, by = stream) + s(DOYres),
                correlation = BestERCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))
```

### Best models
#### Overall
 


lER ~ treatment * stream + treatment * Tanom.iktCs + stream * 
    Tanom.iktCs + s(Qres, by = stream) + s(DOYres, by = stream)
R2 = 0.94
P influences ER in S11, S18, and S6 but not S9.

```{r}
summary(g.er.BEST$gam)
```

Concurvity issues with Qres and DOYres
```{r}
round(concurvity(g.er.BEST$gam, full = FALSE)$estimate,3)
```

```{r}
g.er.BEST.gv <- getViz(g.er.BEST$gam)
check(g.er.BEST.gv)
```


One last check on the autocorrelation. Just foucsing on 3. Some remaining in S9A, S18A
```{r echo= FALSE}
g.er.best.acf <- met %>% 
  mutate(g.erRes = resid(g.er.BEST$lme, type = "normalized")) %>% 
  select(streamTreat, g.erRes) %>% 
  group_by(streamTreat) %>% 
  nest() %>% 
  mutate(acf = map(.x = data, .f = function(d) ggAcf(d$g.erRes) + labs(title = streamTreat)))
```

```{r echo= FALSE}
grid.arrange(grobs = g.er.best.acf$acf, ncol = 3)
```


```{r echo=FALSE}
metBestTest <- met %>% 
  mutate(erres1 = residuals(g.er.BEST$gam, type = "response"),
         erPred1 = predict(g.er.BEST$gam, type = "response"),
         erres2 = residuals(g.er.BEST_t$gam, type = "response"),
         erPred2 = predict(g.er.BEST_t$gam, type = "response"))
```


 Check residuals
Still some signal with doy. Also early dates with S18-P giving problems
Not much of a difference between 1 and 2.
```{r echo=FALSE}
ggplot(metBestTest, aes(y = erres1, x = doy, color = stream, shape = treatment)) +
  geom_point() +
  facet_grid(stream ~ treatment) 
```

```{r echo=FALSE}
ggplot(metBestTest, aes(y = lER, x = erPred1, color = stream, shape = treatment)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1)
```


#### stream temp
lER ~ treatment * Tanom.iktCs + invKT.C.StMean * Tanom.iktCs + 
    invKT.C.StMean * treatment + s(Qres, by = stream) + s(DOYres)
R2 = 0.71
Sig effect of P that depends upon daily T
Daily and stream T combine to decrease?? ER
No interaction between P and stream temp

```{r}
summary(g.er.BEST_t$gam)
```

Looking good
```{r}
round(concurvity(g.er.BEST_t$gam, full = FALSE)$estimate,3)
```

Looks pretty good, issue with one stream
```{r}
g.er.BEST_t.gv <- getViz(g.er.BEST_t$gam)
check(g.er.BEST_t.gv)
```

Still some autocorrelation remaining in S6A, S9A, S9P, S18A
```{r echo= FALSE}
g.er.BEST_t.acf <- met %>% 
  mutate(g.erRes = resid(g.er.BEST_t$lme, type = "normalized")) %>% 
  select(streamTreat, g.erRes) %>% 
  group_by(streamTreat) %>% 
  nest() %>% 
  mutate(acf = map(.x = data, .f = function(d) ggAcf(d$g.erRes) + labs(title = streamTreat)))
```

```{r echo= FALSE}
grid.arrange(grobs = g.er.BEST_t.acf$acf, ncol = 3)
```

```{r echo=FALSE}
ggplot(metBestTest, aes(y = erres2, x = doy, color = stream, shape = treatment)) +
  geom_point() +
  facet_grid(stream ~ treatment) 
```

Not doing a great job with S18
```{r echo=FALSE}
ggplot(metBestTest, aes(y = lER, x = erPred2, color = stream, shape = treatment)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1)
```



### save results
```{r echo = FALSE, include = FALSE}
saveRDS(g.er.BEST,
        file = file.path(here::here("05_SavedModels"), "02a_ER_P_Best.rds"))
saveRDS(g.er.BEST_t,
        file = file.path(here::here("05_SavedModels"), "02a_ER_P_BestTemp.rds"))
```


```{r}
save.image(file.path(here::here("04_SavedImages"), "02c_ERanalysesPonly_rdat"))
```
