---
title: "NEP Analyses"
author: "JMH"
date: "11/19/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo= FALSE}
library(tidyverse)
library(here)
library(mgcViz)
library(MuMIn)
library(mgcv)
library(forecast)
library(gridExtra)
```

# Load & munge data
```{r}
# load(file.path(here::here("04_SavedImages"), "03_GPPanalyses_rdat"))
```


DOY < 183 already removed
```{r message=FALSE, warning=FALSE}
met <- readr::read_csv(file = file.path(here::here("01_Data"),"02_PostERmet.csv")) %>% 
  mutate(stream = fct_relevel(stream, c("st11U", "st18", "st6", "st9")),
         treatment = fct_relevel(treatment, c("ambient", "nitrogen", "phosphorus")),
         Yf = as.factor(Yf),
         streamTreat = as.factor(streamTreat))
```

# NEP Plots
Big differences among treatments. Pretty normal
```{r echo=FALSE}
ggplot(met, aes(y = NEP, x = doy, color = treatment)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(vars(stream))
```

```{r echo=FALSE}
ggplot(met, aes(sample = NEP, color = stream)) +stat_qq() + stat_qq_line() +
  facet_grid(.~stream)
```

# GAMMS

## Determine ARMA model

Preliminary analysis indicated that there was significant autocorrelation. So the first step is to determine the autocorrelation structure. We'll use what is sort of a global model.

```{r}
g.NEP.AC_1.0 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 1,q = 0, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_1.1 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 1,q = 1, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_1.2 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 1,q = 2, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_2.0 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 2,q = 0, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_2.1 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 2,q = 1, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_2.2 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 2,q = 2, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_3.0 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 3,q = 0, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_3.1 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 3,q = 1, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_3.2 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 3,q = 2, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_3.3 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 3,q = 3, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_3.4 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg),
                correlation = corARMA(p = 3,q = 4, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8), niterEM = 1000)

g.NEP.AC_4.0 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 4,q = 0, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

 g.NEP.AC_4.1 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +
                      s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg),
                 correlation = corARMA(p = 4,q = 1, form = ~ doy | streamTreat), REML = FALSE, data = met,
                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

 g.NEP.AC_4.2 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +
                      s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg),
                 correlation = corARMA(p = 4,q = 2, form = ~ doy | streamTreat), REML = FALSE, data = met,
                 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_4.3 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 4,q = 3, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

g.NEP.AC_4.4 <- gamm(NEP ~ treatment + invKT.C.StMean + Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy, by = stream) + s(LightPerDay.lcg), 
                correlation = corARMA(p = 4,q = 4, form = ~ doy | streamTreat), REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000))

```

Model selection indicates that 4_2 is the best model.
```{r echo= FALSE}
model.sel(g.NEP.AC_1.0$lme, g.NEP.AC_1.1$lme, g.NEP.AC_1.2$lme, 
          g.NEP.AC_2.0$lme, g.NEP.AC_2.1$lme, g.NEP.AC_2.2$lme, 
          g.NEP.AC_3.0$lme, g.NEP.AC_3.1$lme, g.NEP.AC_3.2$lme, g.NEP.AC_3.3$lme,
          g.NEP.AC_4.0$lme, 
          g.NEP.AC_4.1$lme,g.NEP.AC_4.2$lme,
          g.NEP.AC_4.3$lme) 
```

ACF: Looks great. One sig lag in S9A, S18N, S18P
```{r echo= FALSE}

# https://www.kaggle.com/timib1203/managing-many-models-with-tidyr-purrr-and-broom
# https://jroy042.github.io/nonlinear/week4.html
# https://stackoverflow.com/questions/47586110/autocorrelation-in-generalized-additive-models-gam
g.NEP.AC_best.acf <- met %>% 
  mutate(g.gppRes = resid(g.NEP.AC_4.2$lme, type = "normalized")) %>% 
  select(streamTreat, g.gppRes) %>% 
  group_by(streamTreat) %>% 
  nest() %>% 
  mutate(acf = map(.x = data, .f = function(d) ggAcf(d$g.gppRes) + labs(title = streamTreat)))
```

```{r echo= FALSE}
grid.arrange(grobs = g.NEP.AC_best.acf$acf, ncol = 3)
```

```{r echo= FALSE}
BestNEPCor <- corARMA(p = 4,q = 2, form = ~ doy | streamTreat)
```



## Model selection
```{r echo=FALSE, include = FALSE}
g.NEP.modsel1t <- uGamm(NEP ~ treatment * invKT.C.StMean * Tanom.iktCs +
                     s(Qres, by = stream) + s(DOYres, by = stream) + s(LightPerDay.lcg),
                correlation = BestNEPCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")

g.NEP.modsel1s <- uGamm(NEP ~ treatment * stream * Tanom.iktCs +
                     s(Qres, by = stream) + s(DOYres, by = stream) + s(LightPerDay.lcg),
                correlation = BestNEPCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")


g.NEP.modsel2t <- uGamm(NEP ~ treatment * invKT.C.StMean * Tanom.iktCs +
                     s(Qres) + s(DOYres, by = stream) + s(LightPerDay.lcg),
                correlation = BestNEPCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")

# these models won't converge, so tried one without full interaction
g.NEP.modsel2s <- uGamm(NEP ~ treatment * stream + stream * Tanom.iktCs + treatment * Tanom.iktCs +
                     s(Qres) + s(DOYres, by = stream) + s(LightPerDay.lcg),
                correlation = BestNEPCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")

# these models won't converge, so tried one without full interaction
g.NEP.modsel3t <- uGamm(NEP ~ treatment * stream + stream * Tanom.iktCs + treatment * Tanom.iktCs +
                     s(Qres, by = stream) + s(DOYres) + s(LightPerDay.lcg),
                correlation = BestNEPCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")

# these models won't converge, so tried one without full interaction
g.NEP.modsel3s <- uGamm(NEP ~ treatment * stream + stream * Tanom.iktCs + treatment * Tanom.iktCs +
                     s(Qres, by = stream) + s(DOYres) + s(LightPerDay.lcg),
                correlation = BestNEPCor, REML = FALSE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8, niterEM = 1000), class = "gamm")

g.NEP.Dredge_1t <-  dredge(global.model = g.NEP.modsel1t, evaluate = TRUE, rank = AIC)
g.NEP.Dredge_1s <-  dredge(global.model = g.NEP.modsel1s, evaluate = TRUE, rank = AIC)
g.NEP.Dredge_2t <-  dredge(global.model = g.NEP.modsel2t, evaluate = TRUE, rank = AIC)
g.NEP.Dredge_2s <-  dredge(global.model = g.NEP.modsel2s, evaluate = TRUE, rank = AIC)
g.NEP.Dredge_3t <-  dredge(global.model = g.NEP.modsel3t, evaluate = TRUE, rank = AIC)
g.NEP.Dredge_3s <-  dredge(global.model = g.NEP.modsel3s, evaluate = TRUE, rank = AIC)
```


```{r echo=FALSE}
g.NEPDredgeSumT1 <- merge(g.NEP.Dredge_1t, g.NEP.Dredge_2t)
g.NEPDredgeSumT2 <- merge(g.NEPDredgeSumT1, g.NEP.Dredge_3t)
g.NEPDredgeSumS1 <- merge(g.NEP.Dredge_1s, g.NEP.Dredge_2s)
g.NEPDredgeSumS2 <- merge(g.NEPDredgeSumS1, g.NEP.Dredge_3s)
g.NEPDredgeSumF <- merge(g.NEPDredgeSumT2, g.NEPDredgeSumS2)
```


All of the models <10 have an interactions between the temps
```{r}
subset(g.gppDredgeSumF, delta <= 2)
subset(g.gppDredgeSumT2, delta <= 2)
```

```{r echo=FALSE}
g.gppBEST1.A <- gamm(lGPP ~ treatment + stream * Tanom.iktCs +   
                     s(Qres, by = stream) + s(doy) + s(LightPerDay.lcg), 
                correlation = BestGPPCor, REML = TRUE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8))
```

```{r echo=FALSE}
g.gppBEST2 <- gamm(lGPP ~ treatment * invKT.C.StMean + treatment * Tanom.iktCs + invKT.C.StMean * Tanom.iktCs +
                     s(Qres, by = stream) + s(doy) + s(LightPerDay.lcg), 
                correlation = BestGPPCor, REML = TRUE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8))
```

```{r echo=FALSE}
g.gppBEST3 <- gamm(lGPP ~ treatment + invKT.C.StMean * Tanom.iktCs +
                     s(Qres, by = stream) + s(doy) + s(LightPerDay.lcg), 
                correlation = BestGPPCor, REML = TRUE, data = met,
                control = lmeControl(maxIter = 1e8, msMaxIter = 1e8))
```

lGPP ~ treatment * invKT.C.StMean * Tanom.iktCs + s(Qres, by = stream) + s(doy) + s(LightPerDay.lcg)
R2 = 0.58
Sig N X stream Temp X daily temp
```{r echo=FALSE}
summary(g.gppBEST1$gam)
```


lGPP ~ treatment * invKT.C.StMean + treatment * Tanom.iktCs + invKT.C.StMean * Tanom.iktCs + s(Qres, by = stream) + s(doy) + s(LightPerDay.lcg)
R2 = 0.57
Sig N * daily temp
Sig stream Temp * daily temp
NS: N * stream Temp
```{r echo=FALSE}
summary(g.gppBEST2$gam)
```

lGPP ~ treatment + invKT.C.StMean * Tanom.iktCs + s(Qres, by = stream) + s(doy) + s(LightPerDay.lcg)
R2 = 0.57
Sig N
Sig stream temp * daily temp - Neg relationship means that as daily temps increase (or 1/temp decreases) the warm streams respond more - i think WANT TO PLOT
```{r echo=FALSE}
summary(g.gppBEST3$gam)
```

Concurvity looks pretty good
```{r echo=FALSE}
round(concurvity(g.gppBEST1$gam, full = FALSE)$estimate,3)
round(concurvity(g.gppBEST2$gam, full = FALSE)$estimate,3)
round(concurvity(g.gppBEST3$gam, full = FALSE)$estimate,3)
```


```{r echo=FALSE}
g.gpp.BEST1.gv <- getViz(g.gppBEST1$gam)
g.gpp.BEST2.gv <- getViz(g.gppBEST2$gam)
g.gpp.BEST3.gv <- getViz(g.gppBEST3$gam)
```

```{r}
check(g.gpp.BEST1.gv)
```

```{r}
check(g.gpp.BEST2.gv)
```

```{r}
check(g.gpp.BEST3.gv)
```

These aren't too useful for interactions
```{r echo=FALSE}
GPPquickPlot1 <- plot(g.gpp.BEST1.gv, allTerms = 1) +
  l_points(color = "pink") + l_fitLine(linetype = 3) + l_fitContour() + 
      l_ciLine(colour = 2) + l_ciBar() + l_fitPoints(size = 1, col = 2) + theme_get() + labs(title = NULL)

  print(GPPquickPlot1, pages = 1)
```

```{r echo=FALSE}
GPPquickPlot2 <- plot(g.gpp.BEST2.gv, allTerms = 1) +
  l_points(color = "pink") + l_fitLine(linetype = 3) + l_fitContour() + 
      l_ciLine(colour = 2) + l_ciBar() + l_fitPoints(size = 1, col = 2) + theme_get() + labs(title = NULL)

  print(GPPquickPlot2, pages = 1)
```

```{r echo=FALSE}
GPPquickPlot3 <- plot(g.gpp.BEST3.gv, allTerms = 1) +
  l_points(color = "pink") + l_fitLine(linetype = 3) + l_fitContour() + 
      l_ciLine(colour = 2) + l_ciBar() + l_fitPoints(size = 1, col = 2) + theme_get() + labs(title = NULL)

  print(GPPquickPlot3, pages = 1)
```



Predict for future ploting
```{r echo= FALSE}
met$GPPgamPred <- predict.gam(g.gppBEST3$gam, met, type = "response")
met$GPPgamPred.se <- predict.gam(g.gppBEST3$gam, met, type = "response", se.fit = TRUE)$se.fit
```

Export
```{r}
readr::write_csv(met, file.path(here::here("01_Data"), "03_PostGPPmet.csv"))
```

```{r}
save.image(file.path(here::here("04_SavedImages"), "04a_NEP_all_rdat"))
# load(file.path(here::here("04_SavedImages"), "03_GPPanalyses_rdat"))
```

